### 2015-12-29 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco report

The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building. During each test, the fire was ignited and the fire developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F). Once this criteria was met, gas cooling began.

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}
There were 14 suppression tests conducted in the single story purpose-built concrete structure. Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the rear of the single story structures and the available ventilation was both through the front doorway. For several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}). The fires were intended to replicate room and contents fires typically seen within residential structures. Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle). Each nozzle flowed 15~s of water or compressed air foam depending on the test. The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack). The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack). Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
	\centering
	\caption{Fire Suppression Test Descriptions}
	\begin{tabular}{llllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Flow Rate			& Fuel           & Ventilation     \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		2 (FSW2)   	&  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
		5 (FSE5)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
		6 (FSW6)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
		7 (FSW7)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
		8 (FSE8)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
		9 (Attic 1) &  Water    &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
		10 (Attic 2)&  CAF      &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
		11 (FSE11)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
		12 (FSW12)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
		13 (FSE13)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
		14 (FSW14)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Test_Descriptions}
\end{table}

Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application on the furniture fuel package after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle (FSE1 in Table~\ref{tab:Test_Descriptions}). The figures provide change in temperature and heat flux measurements at several positions and elevations through the structure: structure doorway, hallway, and three locations within the burn room. These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_1_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_1_Second_Suppression}
\end{figure}

The same fuel load, ventilation, and suppression application durations were also tested with water as the suppression agent (FSW2 in Table~\ref{tab:Test_Descriptions}). Figures~\ref{fig:Test_2_First_Suppression} and \ref{fig:Test_2_Second_Suppression} show the results from these tests.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_2_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_2_Second_Suppression}
\end{figure}

Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression. The remainder of these fire suppression images for both the furniture and wood pallet fuel loads can be found in Appendix~\ref{app:fire_suppression}.

@@

\chapter{Fire Suppression Figures}
\label{app:fire_suppression}

\section{Furniture Fuel Package}
\label{appsubsec:Furniture_Fuel_Package}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, First Suppression}
	\label{fig:Test_3_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, Second Suppression}
	\label{fig:Test_3_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, First Suppression}
	\label{fig:Test_4_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, Second Suppression}
	\label{fig:Test_4_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_5_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_5_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_6_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_6_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_7_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_7_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_8_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_8_Second_Suppression}
\end{figure}

\section{Wood Fuel Package}
\label{appsubsec:Wood_Fuel_Package}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_11_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_11_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_12_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_12_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
	\label{fig:Test_13_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
	\label{fig:Test_13_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_14_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_14_Second_Suppression}
\end{figure}

>>>>

The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building. During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F). Once this criteria was met, gas cooling began.

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
	\caption{Time series of several gas cooling events in a continuous experiment}
	\label{fig:gas_cooling_exp4}
\end{figure}

@@

\section{Fire Suppression}
\label{sec:Fire_Suppression}
There were 14 suppression tests conducted in the single story purpose-built concrete structure. Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}). The fires were intended to replicate room and contents fires typically seen within residential structures. Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle). Each nozzle flowed 15~s of water or compressed air foam depending on the test. The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack). The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack). Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
\centering
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream				& Flow Rate			& Fuel           & Ventilation     \\
\midrule
 1 & CAF~1    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
 3 & CAF~2 	  &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
 4 & Water~2  &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 6 & CAF~3    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 8 & CAF~4    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
12 & CAF~5    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
14 & CAF~6    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAFs tests. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire. These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results}\label{tab:Test_Results}
\begin{tabular}{lccc}
\toprule[1.5pt]
                 & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	         & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 0.15~m (6~in) Above Floor \\
\midrule
CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
Water~2 Room     & 250~$^{\circ}$C - 50~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~3 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression. The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests. This illustrates the impact of gas cooling, indpendent of suppression agent. In several cases rekindling occured, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.

@@
